---
title: "LeapYear_Description"
author: "Nate Heng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LeapYear_Description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r load_devtools, include=FALSE}
library(devtools)
```

```{r load_LeapYear, include=FALSE}
install_github("nheng91/LeapYear")
library(LeapYear)
```

```{r load_data}
load_data("LeapYear")
```

## LeapYear package

This Vignette offers a brief description of how to use the **LeapYear** package.    The **LeapYear** contains only one function: *leap_year()*.  The user must enter a year between 1804 and 2400 and *leap_year()* will notify the user of whether or not the entered year was or will be a leap year. Examples of package use are included in the following documentation.

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Correct Use


```{r}
leap_year(1992)
```

```{r}
leap_year(1993)
```

## Incorrect Use

The user must enter only a single year as the argument.  If multiple years are entered *leap_year()* will produce an error.

```{r}
leap_year(c(1994,1995))
```

The argument entered must also only contain 4 characters.

```{r}
leap_year(20050)
```

The argument entered must also be a number.

```{r}
leap_year("Hello")
```


